Software Development Methodology

### 2024-02-14 latex/ms.tex
.

\section{Code Consistency}
The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
File and directory name whitelisting is enforced with the target of having one file per `technology'.
\dirtree{.0 python/|docs/|latex/.
.1 \texttt{.dockerignore}.
.1 \texttt{.gitignore}.
.1 Dockerfile.
.1 Makefile.
.1 main.py|index.html|ms.tex.
.1 prm/.
.1 pyproject.toml|package.json.
.1 tmp/.
}

@@

>>>>

\section{Code Consistency}
On a higher level the directory should look like this:
\dirtree{%
.1 \texttt{\$HOME/}.
.2 \texttt{\$PLATFORM\_DOMAIN\_NAME/}.
.3 \texttt{\$REPOSITORY\_OWNER/}.
.4 \texttt{\$REPOSITORY\_NAME/}.
}

For example the directory structure that corresponds to the repository that hosts the source code of this paper is:
\dirtree{%
.1 \texttt{\$HOME/}.
.2 \texttt{github.com/}.
.3 \texttt{pbizopoulos/}.
.4 \texttt{software-development-methodology/}.
}

The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
File and directory name whitelisting is enforced with the target of having one file per `technology'.
\dirtree{%
.1 python/|docs/|latex/.
.2 \texttt{.dockerignore}.
.2 \texttt{.gitignore}.
.2 Dockerfile.
.2 Makefile.
.2 main.py|index.html|ms.tex.
.2 prm/.
.2 pyproject.toml|package.json.
.2 tmp/.
}

@@

Code consistency on the directory structure level also brings code portability and also easier execution of commands on multiple repositories.
Using POSIX Utilities we can use the following:
\begin{verbatim}
find $HOME/$DIRECTORY -name $DIRECTORY_OR_FILE |\
xargs dirname |\
xargs -I{} -P0 $COMMAND
\end{verbatim}

For example the following incorporates changes from all \texttt{github.com} remote repositories into the current branches using \texttt{git}:
\begin{verbatim}
find $HOME/github.com -name .git |\
xargs dirname |\
xargs -I{} -P0 git -C {} pull
\end{verbatim}

Another example is to \texttt{make check} all \texttt{github.com} repositories from user \texttt{pbizopoulos}:
\begin{verbatim}
find $HOME/github.com/pbizopoulos/ -name Makefile |\
xargs dirname |\
xargs -I{} -P0 make check -C {}
\end{verbatim}
